|

### 2023-04-09 paper.Rmd
placement of figures 11, 12
fixing spelling in 5.1

Overall, the results show that the conventional tests are more sensitive than the visual test. The conventional tests do have higher power for the patterns they are designed to detect, and generaly unable to detect other patterns. The visual test doesn't require specifiying the pattern ahead of time, relying purely on whether the observed residual plot is detectably different from "good" residual plots. They will perform equally well regardless of the type of model defect. This aligns with the advice of experts on residual analysis, who consider residual plot analysis to be an indispensable tool for diagnosing model problems. What we gain from using a visual test for this purpose is the removal of subjective argument about whether a pattern is visible or not. The lineup protocol provides the calibration of detecting patterns, that if the pattern in the data plot cannot be distinguished from patterns in good residual plots, then no discernible problem with the model exists.

>>>>

Overall, the results show that the conventional tests are more sensitive than the visual test. The conventional tests do have higher power for the patterns they are designed to detect, and are generally unable to detect other patterns. The visual test doesn't require specifying the pattern ahead of time, relying purely on whether the observed residual plot is detectably different from "good" residual plots. They will perform equally well regardless of the type of model defect. This aligns with the advice of experts on residual analysis, who consider residual plot analysis to be an indispensable tool for diagnosing model problems. What we gain from using a visual test for this purpose is the removal of subjective argument about whether a pattern is visible or not. The lineup protocol provides the calibration of detecting patterns, that if the pattern in the data plot cannot be distinguished from patterns in good residual plots, then no discernible problem with the model exists.
